Fully structured proof theory for intuitionistic modal logics

### 2020-06-02 BicolorNS/aiml20/aiml20.tex
improving Sec 4

%Nested sequents were introduced by Kashima \cite{kashima1994cut} and then independently rediscovered by Br\"{u}nnler \cite{brunnler2009deep} and Poggiolesi \cite{poggiolesi2009method}.
%
%Nested sequents are a generalisation of sequents from a multiset of formulas to a tree of multisets of formulas.
%
In standard nested sequent notation, brackets are used to indicate the parent-child relation in the modal accessibility tree. 
%, and can be interpreted as the modal $\BOX$ (similarly to how the comma is interpreted as $\OR$). 
%
Here again, we enhance the structure with a second type of bracketting to encode the preorder relation.
%For intuitionistic logic we need two-sided sequents, which are formally generated by:
%$\Cx \coloncolonequals \lf{A_{1}}, ..., \lf{A_{n}}, \rt{B_{1}},..., \rt{B_{k}}, \BR{\Cx[1]},..., \BR{\Cx[m]}$
%where $\fm{A_{1}}, . . . , \fm{A_{n}}$ are the formulas that would occur on the left of the turnstile if there was a turnstile, $\fm{B_{1}}, . . . , \fm{B_{k}}$ are the formulas that would occur on the right of the turnstile if there was a turnstile, and $\Cx[1], . . . , \Cx[m]$ are nested sequents. We use the $\bullet$ and $\circ$ as polarities indication for formulas.

\begin{definition}
	A two-sided intuitionistic \emph{fully nested sequent} is constructed from the grammar:
	$\Cx \coloncolonequals \varnothing \mid \lf A, \Cx \mid \rt A, \Cx \mid \BR{\Cx} \mid \bBR{\Cx}$,
	%
%	\noindent
	where the $\lf{(\cdot)}$ and $\rt{(\cdot)}$ annotations are used to indicate that the formulas would occur on the left-hand-side or right-hand-side of a sequent respectively in the absence of the sequent arrow. 
\end{definition}

The obtained nested sequent calculus $\nIKp$ is displayed in Figure~\ref{fig:nIK}.
%
The idea is similar to the fully labelled calculus but the shift of paradigm forced us to make different design choices.
%
In particular, the underlying tree-structure prevents us to express the rule $\rn{F_2}$, but its absence is compensated by the \emph{monotonicity rules} $\lrn{mon}$ and $\rrn{mon}$ which were admissible in $\labIKp$.
%
Another beneficial result of this addition is that rules $\rn{refl_\le}$ and $\rn{trans_\le}$ do not need equivalent here.

>>>>

%Nested sequents were introduced by Kashima \cite{kashima1994cut} and then independently rediscovered by Br\"{u}nnler \cite{brunnler2009deep} and Poggiolesi \cite{poggiolesi2009method}.
%
%Nested sequents are a generalisation of sequents from a multiset of formulas to a tree of multisets of formulas.
%
In standard nested sequent notation, brackets $\BR{\cdot}$ are used to indicate the parent-child relation in the modal accessibility tree.
%, and can be interpreted as the modal $\BOX$ (similarly to how the comma is interpreted as $\OR$). 
%
$\lf{(\cdot)}$ and $\rt{(\cdot)}$ annotations are used to indicate that the formulas would occur on the left-hand-side or right-hand-side of a sequent respectively in the absence of the sequent arrow.

To make it fully structured again, we enhance the structure with a second type of bracketting $\bBR{\cdot}$ to encode the preorder relation.
%For intuitionistic logic we need two-sided sequents, which are formally generated by:
%$\Cx \coloncolonequals \lf{A_{1}}, ..., \lf{A_{n}}, \rt{B_{1}},..., \rt{B_{k}}, \BR{\Cx[1]},..., \BR{\Cx[m]}$
%where $\fm{A_{1}}, . . . , \fm{A_{n}}$ are the formulas that would occur on the left of the turnstile if there was a turnstile, $\fm{B_{1}}, . . . , \fm{B_{k}}$ are the formulas that would occur on the right of the turnstile if there was a turnstile, and $\Cx[1], . . . , \Cx[m]$ are nested sequents. We use the $\bullet$ and $\circ$ as polarities indication for formulas.
%

\begin{definition}
	A two-sided intuitionistic \emph{fully nested sequent} is constructed from the grammar:
	$\Cx \coloncolonequals \varnothing \mid \lf A, \Cx \mid \rt A, \Cx \mid \BR{\Cx} \mid \bBR{\Cx}$
\end{definition}

The obtained nested sequent calculus $\nIKp$ is displayed in Figure~\ref{fig:nIK}.
%
The idea is similar to the fully labelled calculus but the shift of paradigm forced us to make different design choices.
%
In particular, the underlying tree-structure prevents us to express the rule $\rn{F_2}$, but its absence is compensated by the \emph{monotonicity rules} $\lrn{mon}$ and $\rrn{mon}$ which were admissible in $\labIKp$.
%
Another beneficial result of this addition is that rules $\rn{refl_\le}$ and $\rn{trans_\le}$ do not need any equivalent here.
